\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-10 paper/subdocuments/results.Rnw
changed fig_equiv to steink not reink

<<setup_data_Brühlhart with and without taxed>>=
# Ohne Nuller
bd <- read.csv("../../data/data_Schweiz.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd$Jahr <- as.numeric(substr(bd$Veranlagungsperiode,1,4))
bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] <- bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] - 2
bd<-bd %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_reink,gini_reinka)
bd<-subset(bd,Jahr<1995 | Jahr >2002)
# 2011 zufügen
bd.2011 <- read.csv("../../data/NP_2011.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011)
levels(bd.0$Veranlagungsperiode)<- c(levels(bd.0$Veranlagungsperiode),"2011")
bd <- rbind(bd,bd.2011[,names(bd)])
bd.long<-reshape(bd,
varying = c("gini_reink","gini_reinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("Net income (only taxed)","Equivalised net income (only taxed)"),
direction ="long")
# mit Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.0<-bd.0 %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_reink,gini_reinka)
bd.0<-subset(bd.0,Jahr<1993 | Jahr >2002)
# 2011 zufügen
bd.0.2011 <- read.csv("../../data/NP_2011_mitnull.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011)
levels(bd.0$Veranlagungsperiode)<- c(levels(bd.0$Veranlagungsperiode),"2011")
bd.0 <- rbind(bd.0,bd.0.2011[,names(bd.0)])
bd.0.long<-reshape(bd.0,
varying = c("gini_reink","gini_reinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("Net income","Equivalised net income"),
direction ="long")
bdlong<-rbind(bd.0.long,bd.long)
names(bdlong)[3]<-"Income"
@

<<equivalencescale, fig.cap='Gini coefficients with and without equivalization',fig.pos='H'>>=
number_ticks <- function(n) {function(limits) pretty(limits, n)}
fig_equiv <- ggplot(bdlong, aes(x=Jahr,y=Gini,shape=Income))+
  scale_y_continuous(limits=c(0.28,0.55))+
  #scale_x_continuous(limits=c(1970,2012),breaks=number_ticks(10)) +
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=Income),size=3)+
  geom_line(data=bdlong,aes(linetype=Income))+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Using (pseudo) equivalence scales")
fig_equiv
# Gini Range
max(bd %>% mutate(d_reink=abs(gini_reink-gini_reinka)) %>% select(starts_with("d_")),na.rm=TRUE)
max(bd.0 %>% mutate(d_reink=abs(gini_reink-gini_reinka)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.012
@

>>>>

<<setup_data_Brühlhart with and without taxed>>=
# Ohne Nuller
bd <- read.csv("../../data/data_Schweiz.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd$Jahr <- as.numeric(substr(bd$Veranlagungsperiode,1,4))
bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] <- bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] - 2
bd<-bd %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd<-subset(bd,Jahr<1995 | Jahr >2002)
# 2011 zufügen
bd.2011 <- read.csv("../../data/NP_2011.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011)%>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd$Veranlagungsperiode)<- c(levels(bd$Veranlagungsperiode),"2011")
bd <- rbind(bd,bd.2011[,names(bd)])
bd.long<-reshape(bd,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income (only taxed)","Equivalised taxable income (only taxed)"),
direction ="long")
# mit Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.0<-bd.0 %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd.0<-subset(bd.0,Jahr<1993 | Jahr >2002)
# 2011 zufügen
bd.0.2011 <- read.csv("../../data/NP_2011_mitnull.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011) %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd.0$Veranlagungsperiode)<- c(levels(bd.0$Veranlagungsperiode),"2011")
bd.0 <- rbind(bd.0,bd.0.2011[,names(bd.0)])
bd.0.long<-reshape(bd.0,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income","Equivalised taxable income"),
direction ="long")
bdlong<-rbind(bd.0.long,bd.long)
names(bdlong)[3]<-"Income"
@

<<equivalencescale, fig.cap='Gini coefficients with and without equivalization',fig.pos='H'>>=
number_ticks <- function(n) {function(limits) pretty(limits, n)}
fig_equiv <- ggplot(bdlong, aes(x=Jahr,y=Gini,shape=Income))+
  scale_y_continuous(limits=c(0.28,0.55))+
  #scale_x_continuous(limits=c(1970,2012),breaks=number_ticks(10)) +
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=Income),size=3)+
  geom_line(data=bdlong,aes(linetype=Income))+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Using (pseudo) equivalence scales")
fig_equiv
# Gini Range
max(bd %>% mutate(d_reink=abs(gini_steink-gini_steinka)) %>% select(starts_with("d_")),na.rm=TRUE)
max(bd.0 %>% mutate(d_reink=abs(gini_steink-gini_steinka)) %>% select(starts_with("d_")),na.rm=TRUE)
# 0.011
@
